\boldmath Commissioning of the highly granular SiW-ECAL technological prototype

### 2018-06-13 performance-paper-draft/longversion/draft.tex
2nd iteration of the long version of the paper. Small correction in the desnity of channels comparison

The SKIROC ASICs can be power-pulsed by taking advantage of the ILC spill structure: 
the bias currents of the ASIC can be switched off during the idle time between bunch trains.
With this method, the ASIC is able to reduce its power consumption down to 25 $\mu$W per channel,
meeting the ILC requirements. All the results shown in this paper are obtained in power pulsing mode.

@@

The readout layers are embedded on a "U" shape carbon structure to protect the wafers.
The full system is then covered by two aluminum plates
to provide electromagnetic shielding and mechanical stability.
This ensemble is denominated SLAB
(``short'' for 1 ASU ensembles or ``long'' for several ASUs enchained) and it can be seen in
Figure \ref{ASU2}.
The PCB thickness is 1.6 alone and 2.7 mm
including the ASICs in its current packaging: 1.1 mm thick LFBGA package.
With these characteristics, a potential density of
3160 channels/dm$^{3}$ is achievable for the baseline design 
of the ILD. This number should be compared with
the density achieved in beam tests with the physics prototype: 1500 channels/dm$^{3}$ \cite{Amjad:2014tha}.

>>>>

The SKIROC ASICs can be power-pulsed by taking advantage of the ILC spill structure: 
the bias currents of the ASIC can be switched off during the idle time between bunch trains.
With this method, the ASIC is able to reduce its power consumption down to 25 $\mu$W per channel,
meeting the ILC requirements. All the results shown in this paper are obtained in power pulsing mode.
This feature is used for all data discussed in this paper
and for first time in long periods of data taking in beam test.

@@

The readout layers are embedded on a "U" shape carbon structure to protect the wafers.
The full system is then covered by two aluminum plates
to provide electromagnetic shielding and mechanical stability.
This ensemble is denominated SLAB
(``short'' for 1 ASU ensembles or ``long'' for several ASUs enchained) and it can be seen in
Figure \ref{ASU2}.
The PCB thickness is 1.6 alone and 2.7 mm
including the ASICs in its current packaging: 1.1 mm thick LFBGA package.
With these characteristics, a potential density of
3160 channels/dm$^{3}$ is achievable for the baseline design 
of the ILD. This number should be compared with
the density achieved in beam tests with the physics prototype: 1500 channels/dm$^{3}$.
With the first versions
of the technollogical prototype we reached similar potential density level waw reached but equipping only a
quarter of the ASUs surface \cite{Amjad:2014tha}.
